---
title: "Learning dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)

```

```{r load data, echo=FALSE}

# read in data set

learning_data <- read_csv2("fake_learning_data.csv",
                           col_names = c("employee",
                                         "organization",
                                         "training",
                                         "training_type",
                                         "learning_hours"),
                           skip = 1)
# worked well
```

# Total Overview {data-icon="fa-sitemap"}

## Column 1 {data-width="100"}

### How to Read this Dashboard  

This is a basic example for a dashboard.
It shows exemplary learning data for an international organization.
The first page ("Corporate Overview") provides insights about learning within the full corporate environment.
The second page ("Results by Company") provides the same information but broken down separately for each company.

## Column 2 {data-width="300"}

### Total Learning Hours {data-height="350"}

```{r}

# get total number of training hours
total_hours <- 172 + 87 + 29

valueBox(total_hours, 
         icon = "fa-pencil",
         color = "blue")

```

### Average Training Hours per Employee {data-height="350"}

```{r}

# create a gauge that shows total training hours by company
## need to aggregate to company 

by_employee <- group_by(learning_data,
                       employee)

# get total training hours by organization, then arrange by number
table_total_training_hours_by_employee <- summarise(by_employee,
                                                   total = mean(learning_hours,
                                                               na.rm = TRUE))

average_hours <- mean(table_total_training_hours_by_employee$total)

# create gauge
gauge(average_hours, min = 0, max = 5, symbol = 'Ø', gaugeSectors(
  success = c(4, 5), warning = c(2.1, 3), danger = c(0, 2)
))


```

### Learning Hours by Training Type {data-height="350"}

```{r}
# create a chart that shows total training hours by training type
## need to aggregate to company 

by_type <- group_by(learning_data,
                       training_type)


# get total training hours by training type, then arrange by number
table_total_training_hours_by_type <- summarise(by_type,
                                                   total = sum(learning_hours,
                                                               na.rm = TRUE)) %>%
  arrange(desc(total))

## create horizontal bar plot

plot_type_1 <- ggplot(table_total_training_hours_by_type,
                 aes(x = reorder(training_type, total),
                     y = total)) +
  geom_col() +
  coord_flip()

plot_type_2 <- plot_type_1 +
    labs(x = "Training Type",
           y = "Total learning hours")

plot_type_2
```



# Results by Company {data-icon="fa-building"}

## Column 1 {data-width=350}

### Umbrella
This column shows data for the company "Umbrella".

### Total Learning Hours

```{r}

# create a chart that shows total training hours by company
## need to aggregate to company 

by_organization <- group_by(learning_data,
                       organization)

# get total training hours by organization, then arrange by number
table_total_training_hours_by_organization <- summarise(by_organization,
                                                   total = sum(learning_hours,
                                                               na.rm = TRUE)) %>%
  arrange(desc(total))

# get total number of training hours
total_hours_umbrella <- 87

valueBox(total_hours_umbrella, 
         icon = "fa-graduation-cap",
         color = "blue")
# one can also set conditions so that the color will depend on the value


```

### Average Training Hours per Employee
```{r}

# create a gauge that shows total training hours by company
## need to aggregate to company 

by_employee <- group_by(learning_data,
                       employee)

# get total training hours by organization, then arrange by number
table_total_training_hours_by_employee <- summarise(by_employee,
                                                   total = mean(learning_hours,
                                                               na.rm = TRUE))

average_hours <- mean(table_total_training_hours_by_employee$total)

# create gauge
gauge(average_hours, min = 0, max = 5, symbol = 'Ø', gaugeSectors(
  success = c(4, 5), warning = c(2.1, 3), danger = c(0, 2)
))


```

### Learning Hours by Organization

```{r}

# create a chart that shows total training hours by company
## need to aggregate to company 

by_organization <- group_by(learning_data,
                       organization)

# get total training hours by organization, then arrange by number
table_total_training_hours_by_organization <- summarise(by_organization,
                                                   total = sum(learning_hours,
                                                               na.rm = TRUE)) %>%
  arrange(desc(total))

## create horizontal bar plot

plot_1 <- ggplot(table_total_training_hours_by_organization,
                 aes(x = reorder(organization, total),
                     y = total)) +
  geom_col() +
  coord_flip()

plot_2 <- plot_1 +
    labs(x = "Organization",
           y = "Total learning hours")

plot_2
```


## Column 2 {data-width=350}

### Fireflies
This column shows data for the company "Fireflies".

### Total Learning Hours

```{r}

# create a chart that shows total training hours by company
## need to aggregate to company 

by_organization <- group_by(learning_data,
                       organization)

# get total training hours by organization, then arrange by number
table_total_training_hours_by_organization <- summarise(by_organization,
                                                   total = sum(learning_hours,
                                                               na.rm = TRUE)) %>%
  arrange(desc(total))

# get total number of training hours
total_hours_fire <- 172

valueBox(total_hours_fire, 
         icon = "fa-graduation-cap",
         color = "orange")
# one can also set conditions so that the color will depend on the value


```


### Average Training Hours per Employee
```{r}

# create a gauge that shows total training hours by company
## need to aggregate to company 

by_employee <- group_by(learning_data,
                       employee)

# get total training hours by organization, then arrange by number
table_total_training_hours_by_employee <- summarise(by_employee,
                                                   total = mean(learning_hours,
                                                               na.rm = TRUE))

average_hours <- mean(table_total_training_hours_by_employee$total)

# create gauge
gauge(average_hours, min = 0, max = 5, symbol = 'Ø', gaugeSectors(
  success = c(4, 5), warning = c(2.1, 3), danger = c(0, 2)
))


```

### Learning Hours by Organization

```{r}

# create a chart that shows total training hours by company
## need to aggregate to company 

by_organization <- group_by(learning_data,
                       organization)

# get total training hours by organization, then arrange by number
table_total_training_hours_by_organization <- summarise(by_organization,
                                                   total = sum(learning_hours,
                                                               na.rm = TRUE)) %>%
  arrange(desc(total))

## create horizontal bar plot

plot_1 <- ggplot(table_total_training_hours_by_organization,
                 aes(x = reorder(organization, total),
                     y = total)) +
  geom_col() +
  coord_flip()

plot_2 <- plot_1 +
    labs(x = "Organization", 
       y = "Total learning hours")

plot_2

# further improvements:
## put values into bars
## color the bars
## remove axis scales
## remove gray background
## put y-axis at top instead of bottom
## Put title to the very top left




```


## Column 3 {data-width=350}

### Nathan Drake Corporation
This column shows data for the company "Nathan Drake Corporation".

### Total Learning Hours

```{r}

# create a chart that shows total training hours by company
## need to aggregate to company 

by_organization <- group_by(learning_data,
                       organization)

# get total training hours by organization, then arrange by number
table_total_training_hours_by_organization <- summarise(by_organization,
                                                   total = sum(learning_hours,
                                                               na.rm = TRUE)) %>%
  arrange(desc(total))

# get total number of training hours
total_hours_drake <- 29

valueBox(total_hours_drake, 
         icon = "fa-graduation-cap",
         color = "green") 
# one can also set conditions so that the color will depend on the value

```

### Average Training Hours per Employee
```{r}

# create a gauge that shows total training hours by company
## need to aggregate to company 

by_employee <- group_by(learning_data,
                       employee)

# get total training hours by organization, then arrange by number
table_total_training_hours_by_employee <- summarise(by_employee,
                                                   total = mean(learning_hours,
                                                               na.rm = TRUE))

average_hours <- mean(table_total_training_hours_by_employee$total)

# create gauge
gauge(average_hours, min = 0, max = 5, symbol = 'Ø', gaugeSectors(
  success = c(4, 5), warning = c(2.1, 3), danger = c(0, 2)
))


```

### Learning Hours by Organization

```{r}

# create a chart that shows total training hours by company
## need to aggregate to company 

by_organization <- group_by(learning_data,
                       organization)

# get total training hours by organization, then arrange by number
table_total_training_hours_by_organization <- summarise(by_organization,
                                                   total = sum(learning_hours,
                                                               na.rm = TRUE)) %>%
  arrange(desc(total))

## create horizontal bar plot

plot_1 <- ggplot(table_total_training_hours_by_organization,
                 aes(x = reorder(organization, total),
                     y = total)) +
  geom_col() +
  coord_flip()

plot_2 <- plot_1 +
    labs(x = "Organization", 
       y = "Total learning hours")

plot_2

```
